Computer Science House Constitution

### 2019-01-17 articles.tex
Update articles.tex
Added James Forcier

Co-Authored-By: saucetray <justinsostreofficial@gmail.com>
Remove the Temporary Amendment
The temporary amendment was taken apart bit by bit until all the useful parts of it were gone. All that remained was the ability to make temporary amendment, made the packet percentage to get an account higher, and disallowed intro members from reapplying/applying past the first week of each semester. I'd like to propose we don't cause this semester's intro members to go through a half-deconstructed process which we will get rid of entirely at the last HM of the se

\asubsection{Responsibilities of the House Secretary}
\begin{enumerate}
	\item To ensure that minutes are recorded and posted for Executive Board Meetings
	\item To ensure that minutes are recorded and posted for House Meetings
	\item To oversee the maintenance of Executive Board records and documents
	\item To provide administrative assistance to the Executive Board
	\item To record all votes cast during House Meetings and Open Executive Board Meetings
\end{enumerate}

@@

% ARTICLE VI - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.

% ARTICLE VII - TEMPORARY AMENDMENTS
\article{Temporary Amendments}
In the case that an amendment should be temporary, the amendment's changes should be listed here. 
Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
\asection{Changes to Evaluations}
During the 2018-2019 period the following will supercede the text otherwise found in this document.
\asubsection{Changes}
\asubsubsection{Removal of Introductory Project}
\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
Additionally, \ref{Introductory Executive Board} will no longer be elected or perform any duties during the described period. 
\asubsubsection{Change of Packet Percentage}
\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations. 
During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
\asubsubsection{Changes to Packet Times}
Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
Each Introductory Member will submit their packet at the end of week 3. 
\asubsubsection{Evaluation Period}
During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
\subsubsection{Referendum}
During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
\end{document}

>>>>

\asubsection{Responsibilities of the House Secretary}
\begin{enumerate}
	\item To ensure that minutes are recorded and posted for Executive Board Meetings
	\item To ensure that minutes are recorded and posted for House Meetings
	\item To oversee the maintenance of Executive Board records and documents
	\item To provide administrative assistance to the Executive Board
	\item To oversee the maintenance of the Activities Information Centers
	\item To record all votes cast during House Meetings and Open Executive Board Meetings
\end{enumerate}

@@

% ARTICLE VI - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}
